TacticToe: Learning to Prove with Tactics

### 2018-08-21 tactictoe_jv.tex
proof planning related work

A closely related approach is proof planning that was firstly describe in 
~\cite{DBLP:conf/cade/Bundy88}. 
Proof planners have been implemented to facilitate interactive theorem proving 
development in Oyster~\cite{DBLP:conf/cade/BundyHHS90},  
Omega~\cite{DBLP:conf/cade/BenzmullerCFFHKKKMMSSS97} and 
\isabelle~\cite{DBLP:conf/cade/DixonF03}.
The philosophy of proof planning is to create (automatically or not) a few 
tactics can prove a wide range of theorems. In this respect, if you consider 
MCTS to be a proof plan then we have produced one general tactic that learns 
from examples and has a large success rate.
But proof planning is also concerned with tactic synthesis where new proof 
plans (tactics in \holfour) may be discovered automatically from examples.
From this point of view, \tactictoe does not look at proof patterns to infer 
new tactics and creates new tactics only by abstracting arguments. Therefore, 
it would be interesting to see how including tactic synthesis or even 
human-designed proof plans in the database 
of tactics $\mathbb{D}_{\mathit{tactic}}$.
Proof planning is a meta approach to tactics constructing more and 
more general tactics by sharing common proof patterns between different tactics.
Comparatively, our approach tries to automate the construction of proof plans 
by letting MCTS policy decide which tactics is the best in each situation. Our 
approach can be thought as one general proof plan only guided by previous human 
proofs. 
our approach does not try to synthetize proof plan automatically but just 
re-use them if they already exists.

>>>>

A closely related approach is proof planning that was firstly describe in 
~\cite{DBLP:conf/cade/Bundy88}. Proof planners have been implemented to 
facilitate interactive theorem proving 
development in Oyster~\cite{DBLP:conf/cade/BundyHHS90},  
Omega~\cite{DBLP:conf/cade/BenzmullerCFFHKKKMMSSS97} and 
\isabelle~\cite{DBLP:conf/cade/DixonF03}.
A proof plan can be seen as a program that given a goal 
returns the appropriate tactic for this goal. From this point of view, 
\tactictoe is a general proof plan that learns to apply the right tactic from 
examples and possess a backtracking mechanism given by the MCTS algorithm.
The philosophy of proof planning is also to create a few 
tactics can prove a wide range of theorems. In this respect, if we omit the 
abstraction technique, \tactictoe is not synthesizing any tactic but simply 
selecting them out of large tactic set. In the end, proof planning methodology 
may become necessary for improving \tactictoe as it provides a way to generate 
tactic applicable to a 
large range of formulas. And more general tactics are usually easier to predict 
accurately by machine learning models as they are associated with more 
(successful) examples in our database.
